---
title: "Mini-Project 3"
author: "Ran Tao, Angela Huang, David Munoz Tord"
output:
  html_document:
    code_folding: hide
---


#Part 1
```{r message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(scales)
library(ggplot2)
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")

```

```{r}
#Join movie-info to title + Filtering only the Western genre movies between 1900 and 2015
western <- "SELECT t.id, t.title, t.production_year AS Year, mi1.info AS Genres
FROM title t
JOIN movie_info AS mi1 ON mi1.movie_id = t.id
WHERE t.production_year IS NOT NULL
AND t.kind_id = 1
AND mi1.info_type_id = 3
AND mi1.info = 'Western'
AND t.production_year
BETWEEN 1900 AND 2015;
"
data <- db %>%
  dbGetQuery(western)

#Figuring out which year had produced more Western movies
data1 <- data %>% group_by(Year) %>% summarise(sum = n()) %>% arrange(desc(sum)) 
head(data1) 


#Plot1: hisotgram with periods 
ggplot(data, aes(Year)) +geom_histogram(binwidth = 1, alpha=.5, position="identity", fill ="#377EB8") + scale_x_continuous(breaks=seq(1900,2010,10), labels=c("1900","1910","1920","1930","1940","1950","1960","1970","1980","1990","2000", "2010")) +
  geom_rect(data=data, aes(xmin=1910, xmax=1914, ymin= -Inf, ymax= +Inf), fill= "red", alpha = 0.002) +
  geom_rect(data=data, aes(xmin=2013, xmax=2015, ymin= -Inf, ymax= +Inf), fill= "red", alpha = 0.002)

```

The term western appeard the first time in july 1912 ev en if the genre was already existing + Westerns were very popular throughout the 1950s. Many of the most acclaimed Westerns were released during this time including High Noon (1952), Shane (1953), The Searchers (1956), and The Wild Bunch (1969). Classic Westerns such as these have been the inspiration for various films about Western-type characters in contemporary settings + the popularity of the Western continued to rise until its peak in the 1950s, when the number of Western films produced outnumbered all other genres combined.

We aim to see the definition of movie in 1950 and 2015 from the perspective of “budget”, “ country” and popularity. We tried to filter out the items “ budget” and “country” from the original dataset and see if there are any trend in these two aspects.

#Part 2
```{r}
# 1) Budget
# Finding the mean budget by joinning movie-info to title to add country and budget info + Filtering only the Western genre movies in the USA
budget <- "SELECT t.id, t.title, t.production_year, mi1.info AS Genres, mi2.info AS Country, mi3.info AS Budget
FROM title t
JOIN movie_info AS mi1 ON mi1.movie_id = t.id
JOIN movie_info AS mi2 ON mi2.movie_id = t.id
JOIN movie_info AS mi3 ON mi3.movie_id = t.id
WHERE production_year IS NOT NULL
AND t.kind_id = 1
AND mi1.info_type_id = 3
AND mi2.info_type_id = 8
AND mi3.info_type_id = 105
AND mi1.info = 'Western'
AND mi2.info = 'USA';
"
data_budget <- db %>%
  dbGetQuery(budget)

# Filtering for 1950
data_budget_1950 <- data_budget %>% filter(production_year == 1950)
# Filtering for 2014
data_budget_2014 <- data_budget %>% filter(production_year == 2014)


# We then downloaded the data and uploaded it again so we could extract the numerical values from the "$" and the "," on the budget column. Finally we just calculated the average (not shown here).

Average_budget_2014 = 3762362
Average_budget_1950 = 1188442

# 2) Country
# Finding the number of non-US western movies by joinning movie-info to title to add country info + Filtering only the Western genre movies outside the USA
country <- "SELECT t.id, t.title, t.production_year, mi1.info AS Genres, mi2.info AS Country
FROM title t
JOIN movie_info AS mi1 ON mi1.movie_id = t.id
JOIN movie_info AS mi2 ON mi2.movie_id = t.id
WHERE production_year IS NOT NULL
AND t.kind_id = 1
AND mi1.info_type_id = 3
AND mi2.info_type_id = 8
AND mi1.info = 'Western'
AND mi2.info <> 'USA';
"
data_country <- db %>%
  dbGetQuery(country)

#Filtering only movie produced in 2014
data_country_2014 <- data_country %>% filter(production_year == 2014)
dim(data_country_2014)

#Filtering only movie produced in 1950
data_country_1950 <- data_country %>% filter(production_year == 1950)
dim(data_country_1950)

# 3) Popularity
#Finding the most popular western movies by joinning movie-info to title to add country and rating info + Filtering only the Western genre movies produced in 2014 only
popularity_2014 <- "SELECT t.title, t.production_year, mi2.info AS Rating
FROM title t
JOIN movie_info AS mi1 ON mi1.movie_id = t.id
JOIN movie_info_idx AS mi2 ON mi2.movie_id = t.id
JOIN movie_info_idx AS mi3 ON mi3.movie_id = t.id
WHERE production_year IS NOT NULL
AND mi3.info > 100000
AND t.kind_id = 1
AND mi1.info_type_id = 3
AND mi2.info_type_id = 101
AND mi1.info = 'Western'
AND production_year = 2014
ORDER BY mi2.info desc
LIMIT 0,10;
"
popularity_2014 <- db %>%
  dbGetQuery(popularity_2014)
head(popularity_2014)

#Finding the most popular western movies by joinning movie-info to title to add country and rating info + Filtering only the Western genre movies produced in 1950 only
popularity_1950 <- "SELECT t.title, t.production_year, mi2.info AS Rating
FROM title t
JOIN movie_info AS mi1 ON mi1.movie_id = t.id
JOIN movie_info_idx AS mi2 ON mi2.movie_id = t.id
JOIN movie_info_idx AS mi3 ON mi3.movie_id = t.id
WHERE production_year IS NOT NULL
AND mi3.info > 100000
AND t.kind_id = 1
AND mi1.info_type_id = 3
AND mi2.info_type_id = 101
AND mi1.info = 'Western'
AND production_year = 1950
ORDER BY mi2.info desc
LIMIT 0,10;
"
popularity_1950 <- db %>%
  dbGetQuery(popularity_1950)
head(popularity_1950)

popularity <- "SELECT t.title, t.production_year, mi2.info AS Rating
FROM title t
JOIN movie_info AS mi1 ON mi1.movie_id = t.id
JOIN movie_info_idx AS mi2 ON mi2.movie_id = t.id
JOIN movie_info_idx AS mi3 ON mi3.movie_id = t.id
WHERE production_year IS NOT NULL
AND mi3.info > 100000
AND t.kind_id = 1
AND mi1.info_type_id = 3
AND mi2.info_type_id = 101
AND mi1.info = 'Western'
ORDER BY mi2.info desc
LIMIT 0,20;
"
popularity <- db %>%
  dbGetQuery(popularity)
head(popularity)

```
Traditionally western films have been strictly about nomadic cowboys and gunfighters set in America in the late 19th century. In recent years, popular western genre movies have incorporated other aspects such as bounty hunters from other countries, LGBT topics, and technology. For Brokeback Mountain, it’s essentially a film about two cowboys that fell in love with each other. This LGBT centered topic would never be publicly shown or even filmed in the 1950s.  Django Unchained (2012) talks about a German dentist buying a African American slave. Many parts of the film shows scenes where Django is a African American cowboy riding a horse. West World (2016), which is a popular series on Netflix, where the setting is in the future with an amusement park of the imagined past such as bounty hunters, cowboys, guns and horse riding. 

In conclusion, we found that the western movie peaks in 1912 and 2004 and the ebb period is between 1975 and 2000. Moreover, for definition of movie, we found that Western movie in 1950 tends to have less budget than western movie in 2015. In addition, from the aspect of country, we found that for 2015 Western movies, there are more movie having different country status, which means one movie produced in different countries. This stands for a more international trend for Western movie in 2015 than in 1950.  


